The importance of measurement uncertainty in ecological management

### 2018-01-08 manuscripts/manuscript.Rmd
drone test

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, dev="CairoPDF", fig.width=7, fig.height=7)
library(tidyverse)
library(gridExtra)
library(ggthemes)
colours <- ptol_pal()(4)
berkeley_colors <- c("#D9661F", "#3B7EA1", "#FDB515", "#6C3302",  "#00B0DA",  "#CFDD45")
```

```{r suggested_libs, message=FALSE}
library(hrbrthemes)
library(ggplot2)
library(Cairo)
library(extrafont)
extrafont::loadfonts()
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```

@@

```{r message=FALSE, warning=FALSE}
read_csv(file.path(log_dir, "ram_ex/ram_ex.csv")) %>% 
  filter(model %in% c("biomass", "catch", "POMDP", "Reed", "pgy")) %>%
   mutate(model = fct_recode(model,
                             "Constant escapement" = "Reed",
                             "TAC" = "pgy"
                             )) %>%
  ggplot(aes(year, stock, col=model)) +
  geom_line(lwd=1) +
  scale_color_manual(values = c("black", "grey", berkeley_colors)) +
  facet_wrap(~commonname, scales = "free", ncol=1) + theme_bw()  
```

>>>>

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7)
library(tidyverse)
library(gridExtra)
library(ggthemes)
colours <- ptol_pal()(4)
berkeley_colors <- c("#D9661F", "#3B7EA1", "#FDB515", "#6C3302",  "#00B0DA",  "#CFDD45")
```

```{r suggested_libs, message=FALSE}
#knitr::opts_chunk$set( dev="CairoPDF")
knitr::opts_chunk$set( dev="cairo_pdf")
library(hrbrthemes)
hrbrthemes::import_roboto_condensed() 
library(ggplot2)
library(Cairo)
library(extrafont)
extrafont::loadfonts()
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```

@@

```{r message=FALSE, warning=FALSE}
ram_ex <- read_csv(file.path(log_dir, "ram_ex/ram_ex.csv"))
ram_ex %>%
  filter(model %in% c("biomass", "catch", "POMDP", "Reed", "pgy")) %>%
   mutate(model = fct_recode(model,
                             "Constant escapement" = "Reed",
                             "TAC" = "pgy"
                             )) %>%
  ggplot(aes(year, stock, col=model)) +
  geom_line(lwd=1) +
  scale_color_manual(values = c("black", "grey", berkeley_colors)) +
  facet_wrap(~commonname, scales = "free", ncol=1) + theme_bw()  
```
